\renewcommand{\super}{Dr. Jessica A. Grahn} %supervisor
\renewcommand{\superj}{Dr. Adrian M. Owen} %joint supervisor, if there is one, leave blank if not (lbin)... only one of the three.
\renewcommand{\superc}{} %co-supervisor, if there is one, leave blank if not (lbin)
\renewcommand{\supera}{} %alternate supervisor, if there is one, leave blank if not (lbin)
\renewcommand{\sco}{}  %member of supervisory committee
\renewcommand{\sct}{}  %other member of supervisory committee (lbin)
\renewcommand{\examo}{Dr. Marc Joanisse}  %examining committee (up to four, if less leave blank)
\renewcommand{\examt}{Dr. Ingrid Johnsrude}
\renewcommand{\examth}{Dr. Mark Daley}
%\renewcommand{\examf}{}
\renewcommand{\department}{Department of Psychology}
\renewcommand{\degree}{Masters of Science}
\renewcommand{\firstname}{Avital}
\renewcommand{\lastname}{Sternin}
\renewcommand{\titl}{Classifying music perception and imagination using EEG}
%\renewcommand{\spinetitle}{}%only if the above is more than 60 characters
\renewcommand{\thesisformat}{Monograph} %or Integrated Article
%\renewcommand{\gyear}{\number\year}
%\newcommand{\makecoauthor}{
%Type information about coauthorship here/ }
\renewcommand{\makeacknowledge} {
%Type in acknowledgements here
I would like to thank my supervisors, Dr. Jessica Grahn and Dr. Adrian Owen for guiding me through this project. 
Without their support and encouragement this document would not be in your hands today.

I would like to thank Dr. Sebastian Stober for pushing me to explore new and difficult areas, and for being patient with me when things didn't stick the first time around.
Without Sebastian this project would not exist. 

To the lab members in the Owen and Grahn Labs: Thank you for your invaluable  suggestions, feedback, and assistance at all stages of this experiment.

I would also like to thank those who shared the first floor of the Brain and Mind Institute. 
Thank you for being there to discuss science and grapple with difficult concepts while being the kindest friends one could ask for. 

Lastly, I want to thank my family for supporting me in this endeavour.
Especially my father, for teaching me what good science is.
}
%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}
\maketitle
\addcontentsline{toc}{chapter}{Certificate of Examination}
\makecert
\newpage
%\addcontentsline{toc}{chapter}{Co-Authorship Statement}
%\coauthor{\makecoauthor}  %comment this out if none
%\newpage
\addcontentsline{toc}{chapter}{Abstract}
\Large\begin{center}\textbf{Abstract}\end{center}\normalsize
\begin{spacing}{2}
%%  ***  Put your Abstract here.   ***
%% (150 words for M.Sc. and 350 words for Ph.D.)
This study explored whether we could accurately classify perceived and imagined musical stimuli from EEG data. 
Successful EEG-based classification of what an individual is imagining could pave the way for novel communication techniques, such as brain-computer interfaces. 
We recorded EEG with a 64-channel BioSemi system while participants heard or imagined the different musical stimuli. 
Using principal components analysis, we identified components common to both the perception and imagination conditions however, the time courses of the components did not allow for stimuli classification. 
We then applied deep learning techniques using artificial neural networks. 
This technique enabled us to classify perception of music at a statistically significant level (28.7\%), but we were unable to classify imagination of music (7.41\%). 
The next step is to determine which characteristics of music are driving perception classification rates and to capitalize on them to raise imagination classification rates. 
\end{spacing}
\vfill
\textbf{Keywords:} music perception, music imagination, classification, electroencephalography (EEG), machine learning, deep learning, brain-computer interface (BCI)
\newpage
\addcontentsline{toc}{chapter}{Acknowledgements}
\acknowledge{\makeacknowledge}	%as above
\newpage
\tableofcontents
\newpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\newpage
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables\newpage
\addcontentsline{toc}{chapter}{List of Appendices}
\listofmyappendices\newpage
%\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
%\large List of Abbreviations, Symbols, and Nomenclature \normalsize
%\newpage
% make sure to begin the regular text on the right-hand side
% p.1 is the ODD side, wider margin on th eleft in double-sided
\cleardoublepage
\end{preliminary}